Did WW2 Produce an Equivalent to a Modern Computer?

### 2017-02-23 Draft 2/Master.tex
Added Turing Machines section
(empty); Fixed numbering
Misc changes
Ngl thats the best you're getting
Loooooads of nice nice changes
Cba to explain I havn't been commiting regularly
Added recursive syntax
Insignificant tiny changes which I can't place
sec1: renamed R function to Y combinator
Fixed list end collection
Proof read sec1&2
Lots of lovely changes

\documentclass {article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{subfiles}
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\title{How Significant was WW2 in the Development of the Computer?}
\date{November 24, 2016}
\author{Max Penrose}

\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents

\section{Effective Computability}

In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'. Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'. However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.

\subsection{Church's $\lambda$-Calculus}

@@

>>>>

\documentclass {article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{subfiles}
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{multirow, bigdelim}
\usepackage{hhline}
\usepackage{tabu}	
\usepackage[bb=boondox]{mathalfa}
\usepackage{yfonts}
\usepackage{cleveref}
\usepackage{listings}

\title{Did WW2 Produce an Equivalent to a Modern Computer?}
\date{February 23, 2017}
\author{Max Penrose}

\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents
\clearpage

\section{Church's $\lambda$-Calculus}

@@

\section{Turing Machines}

\subfile{"Section 2 - Turing Machines"}

\section{Universality}

\subfile{"Section 3 - Universality"}

### 2017-02-23 Draft 2/Section 3 - Universality.tex
Proof read sec1&2
Lots of lovely changes

\renewcommand{\arraystretch}{1.5}p
So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching. Unfortunatley, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions. The easiest way of doing this is by assuming that a certain system can perform every operation a computer can perform. For this purpose, we will choose Turing machines, for purposes that will become clear later. Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing FSM.

>>>>

\renewcommand{\arraystretch}{1.5}
So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching. Unfortunatley, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions. The easiest way of doing this is by assuming that a certain system can perform every operation a computer can perform. For this purpose, we will choose Turing machines, for purposes that will become clear later. Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing FSM.
